Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
fixed caption label in subfigs
Fix a typo in orcid.

\author{Shengyi Wang}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~shengyiw} }{shengyiw@cs.princeton.edu}{https://orcid.org/[0000-0002-2286-8703}{}

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.48\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
			\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional}} 
			\label{traverse_lock_a}	
		\end{subfigure}
		\\ \\ 
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=C, style=myStyle]{lock_insert.c} 
			\caption{The \lstinline{insert} method of the lock-coupling template algorithm written in C}
			\label{insert_lock}	
		\end{subfigure}
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms \wm{I like the layout here, but it would make more sense if \lstinline{traverse} was b and \lstinline{insert} was c}}
	\label{traverse_lock}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.48\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=caml, style=myStyle]{giveup_traverse.ml} 
			\caption{The \lstinline{traverse} method of the give-up template algorithm written in an ML-like language}
			\label{traverse_giveup_a}	
		\end{subfigure}
		\\ \\ 
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=C, style=myStyle]{giveup_insert.c} 
			\caption{The \lstinline{insert} method of the give-up template algorithm written in C}
			\label{insert_giveup}	
		\end{subfigure}
	\end{subfigure}\qquad
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{giveup_traverse.c} 
		\caption{The \lstinline{traverse} method of the give-up template algorithm written in C}
		\label{traverse_giveup_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} and \lstinline{insert} methods of the give-up template algorithms}
	\label{traverse_giveup}
\end{figure}

>>>>

\author{Shengyi Wang}{Princeton University, USA \and \url{https://www.cs.princeton.edu/~shengyiw} }{shengyiw@cs.princeton.edu}{https://orcid.org/0000-0002-2286-8703}{}

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.48\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=caml, style=myStyle]{lock_traverse.ml} 
			\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in an ML-like language \cite{krishna2019compositional}} 
			\label{traverse_lock_a}	
		\end{subfigure}
		\\ \\ 
		\renewcommand{\thesubfigure}{c}% New fixed/manual numbering
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=C, style=myStyle]{lock_insert.c} 
			\caption{The \lstinline{insert} method of the lock-coupling template algorithm written in C}
			\label{insert_lock}	
		\end{subfigure}
	\end{subfigure}\qquad
	\renewcommand{\thesubfigure}{b}% New fixed/manual numbering
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{lock_traverse.c} 
		\caption{The \lstinline{traverse} method of the lock-coupling template algorithm written in C}
		\label{traverse_lock_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} method of the lock-coupling template algorithms 
		%\wm{I like the layout here, but it would make more sense if \lstinline{traverse} was b and \lstinline{insert} was c}
	}
	\label{traverse_lock}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.48\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=caml, style=myStyle]{giveup_traverse.ml} 
			\caption{The \lstinline{traverse} method of the give-up template algorithm written in an ML-like language}
			\label{traverse_giveup_a}	
		\end{subfigure}
		\\ \\ 
		\renewcommand{\thesubfigure}{c}% New fixed/manual numbering
		\begin{subfigure}[t]{\textwidth}
			\lstinputlisting[language=C, style=myStyle]{giveup_insert.c} 
			\caption{The \lstinline{insert} method of the give-up template algorithm written in C}
			\label{insert_giveup}	
		\end{subfigure}
	\end{subfigure}\qquad
	\renewcommand{\thesubfigure}{b}% New fixed/manual numbering
	\begin{subfigure}[t]{0.48\textwidth}
		\lstinputlisting[language=C, style=myStyle]{giveup_traverse.c} 
		\caption{The \lstinline{traverse} method of the give-up template algorithm written in C}
		\label{traverse_giveup_b}
	\end{subfigure}
	\caption{The \lstinline{traverse} and \lstinline{insert} methods of the give-up template algorithms}
	\label{traverse_giveup}
\end{figure}
